Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Remove extra whitespace
paper: Add shortlists section

>>>>

Like embeddings, shortlists also provide a way to reduce the computational
complexity, but this time at the output layer instead of the inference layer
\cite{schwenk05}. In the shortlist we pick the $n$ most frequent words in the
corpus and $n$ output units to those $n$ words in the corpus, predicting every
other uncommon word as an unknown token. However, input encodings still
allow for representations of those words deemed uncommon, either by
embeddings or one-hot encoding.

The overall theory behind shortlists is that any optimal model operates
on a pareto principle, 20% of the words which are the most frequent will
be predicted roughly 80% of the time. Since the computation of the output
encodings of height $|V|$ is a fixed cost on every training and inference
cycle, the user of the model is paying for the capacity to predict words which
will seldomly be predicted. A good shortlist should be able to substantially
reduce the computational complexity of the model whilst still retaining a
relatively high degree of accuracy.
